Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-11 Chapter-1/1-Theory.tex
s

A summary of the pion final states in order of pion multiplicity is given in table \ref{tab:pionFinal}. Pion capture on the argon orbital and pion decay at rest dominate the cross section under 100 MeV. The pion decay life time is $\tau_\pi = 2.6 \times 10^-8$ s and the main decay mode is  $\pi^-\rightarrow \mu^- + \bar\nu_\mu$ (BR 99.98\%); for pion decay at rest, the muon is emitted with an energy of $\sim5$ MeV and it decays into $\mu^-\rightarrow e^- + \bar\nu_e + \nu_\mu$ in $\tau_\mu = 2.3 $ $\mu$s . Since pion capture can be considered an electromagnetic process and pion decay is a weak process, this energy region is purposely excluded from the hadronic cross section measurement.

>>>>

A summary of the pion final states in order of pion multiplicity is given in table \ref{tab:pionFinal}. Pion capture and pion decay at rest dominate the cross section under 100 MeV. We define pion capture as the process determining the formation of a pionic atom and the subsequent pion's end of life. Stopping negative pions can form pionic argon, where the negative pion plays the role of an orbital electron. Since the pion mass is two orders of magnitude greater than the electron mass, the spatial wave function of the pion will overlap way more with the nucleus compared to the electron case. After the electromagnetic formation of the pionic atom, the pion will quickly absorbed by the nucleus, which is put in an excited state. The nucleus then de-excite with the emission of low energy nucleons and photons.  Pion capture is predominant compared to pion decay, the other important process for very low energy pions. The decay of a pion is governed by the weak force; the pion decay life time is $\tau_\pi = 2.6 \times 10^{-8}$ s and the main decay mode is  $\pi^-\rightarrow \mu^- + \bar\nu_\mu$ (BR 99.98\%). %; for pion decay at rest, the muon is emitted with an energy of $\sim5$ MeV and it decays into $\mu^-\rightarrow e^- + \bar\nu_e + \nu_\mu$ in $\tau_\mu = 2.3 $ $\mu$s. 
 Since pion capture can be considered an electromagnetic process and pion decay is a weak process, this energy region is purposely excluded from the hadronic cross section measurement.
